Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
Conclusion

\subsection{Central Server}
The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Game} instances and the {\em Therapist Portal}. It is written in Node JS and stores data in a MongoDB instance. We also do audio encoding to create playable audio files from child microphone data obtained from {\em Kimbee Game} instances.

@@

[Conclusion Here]

>>>>

\subsection{Central Server}
The {\em Central Server}, see Figure \ref{fig:tech}, faciliates communication between all the {\em Game} instances and the {\em Therapist Portal}. It is written in Node JS and stores data in a MongoDB instance. We also do audio encoding to create playable audio files from child microphone data obtained from {\em Game} instances.

@@

To conclude, {\em Kimbee} is an application which uses speech recognition to help children and speech therapists better remedy speech impediments. While it currently only focuses on `R' to `W' sounds, it can be further expanded to supplement therapy by giving a therapist the recordings of a child in a remote setting and by giving a child the opportunity to practice more than the short time period allotted weekly. By giving children an enjoyable speech therapy tool we hope to save money the money of both schools and parents while simultaneously giving children a better education by helping them overcome their speech impediment as quickly as possible.
